Visually pleasing knot projections

### 2021-09-14 inst/jma_rebuttal.tex

P4, line 18: A gentle introduction to ``R" would help to make the
following easier to understand.

P4, lines 27-32: What is the meaning of this? - Six points defining
two handle pairs?  (Why the extreme precision with 8 digits?)

Figure 3: What is the color assignment? - one color for each Bezier
segment?  How many circles are drawn for each segment?  (Say that
solid blotches result from densely overlapping circles.)

\textcolor{blue}{The original caption was lacking detail.
  \begin{description}
  \item[OLD text] ``The \emph{path} of (unoptimized) knot~$7_6$,
    showing Bezier handles as thin straight lines and circles.  The
    coloured circles have a radius proportional to the curvature (that
    is, the reciprocal of the radius of curvature) along the strand;
    note large curvature at loop on left"
  \item[NEW text] ``The \emph{path} of (unoptimized) knot~$7_6$,
    showing Bezier handles as thin straight lines and circles.  The
    coloured circles have a radius proportional to the curvature (that
    is, the reciprocal of the radius of curvature) along the strand.
    Colouring is arbitrary, one color for each Bezier segment; solid
    blotches result from densely overlapping circles.  Note large
    curvature at loop on left"
  \end{description}
  Each segment has one circle per control point (which defaults to
  $n=100$) but this is user-settable.
}

### 2021-09-14 inst/jma_knot.tex
fixes issue #27

\begin{figure}[htbp]
  \begin{center}
\begin{verbatim}
> k76_rough <- reader(system.file("7_6_first_draft.svg",package="knotR"))
> knotplot2(k76_rough, seg=TRUE)
\end{verbatim}
\begin{centering}
\includegraphics[scale = 0.9]{knot-7_6_rough}
\caption{The \emph{path} of (unoptimized) \label{7_6_rough}
  knot~$7_6$, showing Bezier handles as thin straight lines and
  circles.  The coloured circles have a radius  proportional to the
  curvature (that is, the reciprocal of the radius of curvature) along
  the strand; note large curvature at loop on left}
  \end{centering}
  \end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
\begin{verbatim}
> k76_rough <- reader(system.file("7_6_first_draft.svg",package="knotR"))
> knotplot2(k76_rough, seg=TRUE)
\end{verbatim}

\begin{centering}
\includegraphics[scale = 0.9]{knot-7_6_rough}
\caption{The \emph{path} of (unoptimized) \label{7_6_rough}
  knot~$7_6$, showing Bezier handles as thin straight lines and
  circles.  The coloured circles have a radius proportional to the
  curvature (that is, the reciprocal of the radius of curvature) along
  the strand.  Colouring is arbitrary, one color for each Bezier
  segment; solid blotches result from densely overlapping circles.
  Note large curvature at loop on left}
  \end{centering}
  \end{center}
\end{figure}
